Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Use proper word

Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not cipher messages or can be easily compromised exposing information} are less than

>>>>

Technology or Engineering that started using safer alternatives \footnote{\textcolor{blue}{This addresses the issue of insecure/unsafe applications which do not encrypt messages or can be easily compromised exposing information}} are less than
